State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
small edit to paper
make things pretty
got rid of the old version of the LS

\subfigure[]{\includegraphics[scale=0.7]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta2Convergence.pdf}}

@@

@@

\section{Parameter Estimation Using Least Squares}\label{LeastSquaresAppendix} 
The finite state space model  given in \ref{eq:ReducedForm} is linear in parameters and therefore Least Square (LS) method can be applied to estimate the unknown parameters. We define $L \times n_{\theta}$ matrix
\begin{eqnarray}\label{eq:QMatrix}
	\lefteqn {\mathbf{Q}(\mathbf{x}_t)=} \\
&&\boldsymbol{\Gamma}^{ - 1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r}) \int_\Omega {f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t)\boldsymbol{\psi}^{\top} \left(\mathbf{r}-\mathbf{r}'\right)d\mathbf{r}'} d\mathbf{r}}\nonumber
\end{eqnarray}
by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} and using $\xi = 1-\zeta T_s$ at each time instant we can write
\begin{eqnarray}
	\mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\zeta T_s\mathbf x_0+\mathbf e_0 \nonumber \\
	\mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\zeta T_s\mathbf x_1+\mathbf e_1\nonumber\\
	&\vdots& \\
	\mathbf x_{T}&=&\mathbf x_{T-1}+T_s \mathbf Q(\mathbf x_{T-1}) \boldsymbol{\theta}-\zeta T_s\mathbf x_{T-1}+\mathbf e_{T-1} \nonumber
\end{eqnarray}
% in matrix form 
% \begin{equation}
% 	\left[
% 	\begin{array}{cccc}
% 		\mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}
% 	\end{array}
% 	\right] -\left[
% 	\begin{array}{cccc}
% 		\mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}
% 	\end{array}
% 	\right] =T_s\left[
% 	\begin{array}{cc}
% 		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
% 		\mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}
% 	\end{array}
% 	\right] \left[
% 	\begin{array}{cc}
% 		\boldsymbol{\theta} \\
% 		\zeta
% 	\end{array}
% 	\right]+\left[
% 	\begin{array}{cccc}
% 		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
% 	\end{array}
% 	\right] 
% \end{equation}
 in compact form we have 
\begin{equation}
	\mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi 
\end{equation}
where 
\begin{small}
\begin{equation*}
	\mathbf Z=\left[
	\begin{array}{cccc}
		\mathbf x_{1}-\mathbf x_{0}\\
		\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
		\mathbf x_{T}-\mathbf x_{T-1}
	\end{array}
	\right],\quad \mathbf X=T_s\left[
	\begin{array}{cccc}
		\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
		\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\
		\mathbf Q(\mathbf x_{T-1})&-\mathbf x_{T-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
and
\begin{small}
\begin{equation*}
\quad \mathbf W=\left[
	\begin{array}{cc}
		\boldsymbol{\theta} \\
		\zeta
	\end{array}
	\right],\quad \boldsymbol \xi=\left[
	\begin{array}{cccc}
		\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
using the LS method $ \mathbf W$ can be estimated 
\begin{equation}
	\mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z 
\end{equation}

\section{Parameter Estimation Using Least Squares - Dean}\label{App:LeastSquaresAppendix} 

>>>>

\begin{figure*}[th]
\subfigure[]{\includegraphics[scale=0.5]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta0Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta2Convergence.pdf}}

@@

\end{figure*}

@@

\section{Parameter Estimation Using Least Squares}\label{App:LeastSquaresAppendix} 
